---
title: "Chapter 14 Exercise"
output: html_notebook
Name: Daniel Lee
---

Setup
```{r}
library(mosaic)
library(DataComputing)
library(tidyverse)
```


### Problem 14.1
```{r}
mosaicData::CPS85 %>%
  ggplot(aes(x = sex, y = wage)) +
  geom_boxplot(aes(fill=sex))
```


### Problem 14.2
- Approximately 1.63 meters

### Problem 14.3
Women = less than 1.6 meters
Men = Around 1.75 meters

### Problem 14.4
40 years old = around 27 bmi 
70 years old = around 28 bmi

### Problem 14.5
Graph A
```{r}
CPS85 %>%
  ggplot(aes(x=wage)) +
  geom_density(aes(fill=sex, color=sex), alpha=0.5) +
  facet_grid(.~married) +
  ggtitle("(A)") + xlim(0,30)
```

Graph B
```{r}
CPS85 %>%
  ggplot(aes(x=age, y=wage)) +
  geom_smooth(aes(color=sex)) +
  ggtitle("(B)") +
  facet_grid(married ~.) + ylim(0,NA)
```

Graph C
```{r}
CPS85 %>%
  ggplot(aes(x=age, y=wage)) +
  ggtitle("(C)") +
  geom_smooth(aes(color=sex)) +
  facet_wrap(~ sector) + ylim(0,25)
```

### Problem 14.6
```{r}
mosaicData::CPS85 %>%
  ggplot(aes(x = sector, y =wage, color = sex)) +
  geom_boxplot() +
  ylim(0,25)
```

### Problem 14.7
```{r}
mosaicData::CPS85 %>%
  ggplot(aes(x = educ, y =wage, color = sex)) +
  geom_point() +
  stat_smooth(method="lm") +
  ylim(0,15)
```

### Problem 14.8
```{r}
mosaicData::Galton %>%
  ggplot(aes(x = height, y = mother)) +
  geom_density2d() +
  facet_grid(~ sex)
```

### Problem 14.9
a) It is not fully consistent with the data
b) 1:4
c) Yes

### Problem 14.10
```{r}
mosaicData::Galton %>%
  ggplot(aes(x=height)) +
  geom_density(aes(fill=sex, color=sex), alpha=0.5) +
  xlim(55,80)
```

### Problem 14.11
a) As the incomeGroup increases, the range of percentage of fraction 65 and older decreases with a outlier when the incomeGroup is around 58000. 

b) Yes, it follows the 1/square root n rule. 

### Problem 14.12
```{r}
MedicareCharges %>%
  ggplot(aes(x = drg)) +
  geom_density()
```


### Problem 14.13
```{r}
Heights <-
  NCHS %>%
  filter(age > 20, ! is.na(smoker)) %>%
  group_by(sex, smoker, age) %>%
  summarise(height = mean(height, na.rm=TRUE))

Heights %>%
  ggplot(aes(x = age, y = height)) +
  geom_line(aes(linetype = smoker)) +
  facet_wrap(~ sex) +
  stat_smooth(method = lm)
```
For female, the smokers and non-smokers differ differently at the age of around 35 years old.
For male, the smokers and non-smokers differ differenrlty at the age of around 60 years old.
